NN Portfolio Optimierung

### 2024-02-15 paper/Paper.tex
add dist evaluations to results

@@

            \begin{figure}[ht]

@@

            \end{figure}

@@

            In the end, four classes were kept, bar chart, diagram, graph, and pie chart, 
            so the total images now used were 7,753. 
            he images came in various dimensions and were resized to the natural images 32x32 and converted to JPG format. 
            I’ll note here that JPG was chosen because it only has 3 color channels and no alpha channel. 
            If PNG is used then it could have a shape of (32,32,4) which adds unnecessary parameters for the scope of my objectives.
            See Figure \ref{scraped-overview} for examples.

            \begin{figure}[ht]

@@

            Early on, I pre-identified possible misclassifications once I scanned through the set of generated graphs. 
            The similarities between some of the graphs, especially the log-normal and normal distribution, were considerable. 
            They were not ‘duds’ like previously mentioned -- they looked typical, but because of the density functions’ parameters, 
            they were similar in appearance to a point where it would become a 50-50 decision if I had to classify them myself. 
            The cases when this happened are a minority, but it was important to keep this in mind as I evaluated the models later.
            See Figure \ref{generated-overview} for examples. The density functions that created the random variables in the graph
            are listed below.

            \begin{figure}[ht]

@@

            The ANN process used in my model is called a feed-forward neural network or FNN. 
            The structure of the model consists of three parts and are shown in Figure \ref{nn-bishop}: 
            an input layer, one or many hidden layers consisting of neurons, and an output layer. 
            The two main processes in the model are forward-propagation and back-propagation, 
            and can be summed up by their respective goals, producing an estimate and minimizing the loss. 
            Forward-propagation begins once the model is built and the data is split into the input values x and the target values y. 
            In this scenario the goal is to use x to predict y.

@@

                The most important parts of a CNN are its convolutional layers and pooling layers 
                since they are the means in which the original image gets ‘boiled down’ into its ‘essence’.
                I use this analogy because one can imagine a set of ingredients, pixels making up an image, 
                that get thrown into a boiling pot where the water evaporates leaving only the important flavors behind. 
                This visceral example can be summed up more literally, 
                where the original image gets transformed layer by layer from the original pixel values to the final class scores. 
                By the end, the full image will be reduced into a single vector of class scores, arranged along the depth dimension. 
                What are these class scores? They indicate the estimate for each class or y target. 
                As an example, the final output layer for CIFAR-10 would have dimensions of (1, 1, 10) 
                since it has a total of 10 classes that an image can be sorted into \cite{cs231n2023} -- airplane, dog, cat, etc.
                The step by step process can be seen more clearly in Figure \ref{cnn-overview-fig},
                where the input image of car will be transformed into the most important features and then classified as a car.

                \begin{figure}[ht]

@@

                \textbf{Output Volume Size Equation:}

@@

            The implementation of this project wouldn’t be possible without the various tools used. 
            I’ll describe them all briefly and list out the versions used for the sake of reproducibility in Table \ref{py-versions}. 
            TensorFlow \cite{abadi2016-tensorflow} is an end-to-end platform for building machine learning models 
            and that works with Keras \cite{chollet2015-keras}, which is a deep learning API written in Python connected to TensorFlow, 
            to create all of the models in this project. 
            Python comes with a plethora of libraries to make working with data and images easier. 
            First there is NumPy \cite{harris2020-numpy} -- a math library with powerful ndarrays. 
            Then there is pandas \cite{reback2020-pandas} \cite{mckinney2010-pandas} 
            which allows for the creation and manipulation of dataframes, which themselves are made up of NumPy’s arrays. 
            The next important library is Matplotlib \cite{hunter2007-matplotlib} 
            where all of the generated graphs used in the models were plotted. 
            Lastly, one of the most important libraires for image classification using TensorFlow 
            and Keras is Pillow \cite{clark2015pillow} since it allows the user to manipulate individual pixels of an image using Python. 
            The PIL Image is a class that can be used and returned using TensorFlow.

@@

            In total, four simple graph classifiers were created -- each with a specific purpose of evaluation in mind. 
            The idea behind them was to create a base assumption that the graphs I generated can be considered a realistic dataset 
            one could get if they scraped from various sources. 
            The main goal is to be able to classify graphs into their probability distribution, 
            but this step acts as a bridge and quality assurance for the generated graph dataset 
            which will be used in the distribution graph classifiers. 
            Each model has a specific name consisting of acronyms to distinguish itself: 
            CIFAR is the natural images, SCP is the scraped graphs, GEN stands for the generated graphs, 
            and 1 indicates the model structure. This results in the four models: CIFAR\_SCP\_1, CIFAR\_GEN\_1, GEN\_SCP\_1, 
            and CIFAR\_GEN\_SCP\_1. The model struture for all classifiers is shown by layer in Table \ref{model-layer-info}.

@@

            The second model, much like the first one, answers the question: 
            are the generated graphs distinguishable from the natural images as well? 
            This was the first test for the generated graphs and much like the first model, 
            should have achieved high accuracy. The main question here would be the difference in accuracy between CIFAR\_SCP\_1 
            and CIFAR\_GEN\_1 since a higher accuracy in the former would indicate 
            that my generated graphs have some similarities with natural images that are not apparent in the scraped graphs. 
            This could be turned around and a much higher accuracy in CIFAR\_GEN\_1 could indicate 
            that one of my original theories about the scraped dataset could be correct 
            and that is the ‘graph-like’ nature of the images in the scraped dataset which are more artistic 
            or non-numerical representations of graphs. 
            In Table \ref{cifar-graphs-1}, one can see that the input in CIFAR\_SCP\_1 and CIFAR\_GEN\_1 are balanced.

@@

            Lastly, all of the datasets were used in a model to classify them as natural, generated, or scraped. 
            The outcome of this would not be as important as the first three, 
            but it would have reinforced the previous intermediate conclusions about the nature of the datasets. 
            A very high accuracy would have meant all datasets are highly distinguishable from one another 
            and point towards tweaking the generated graphs. The information for GEN\_SCP\_1 and CIFAR\_GEN\_SCP\_1
            can be seen in Table \ref{cifar-gen-scp-1}.

@@

            The images used, total number of images, training images, validation images, 
            and model structure are all the same, except for the dimensions of the image and that can be seen in Table \ref{dist-dims-1}.
            The reason for this is how much information is lost when the image is 32x32. 
            It was easy to assume that the model would perform poorly when the density function line almost completely disappears. 
            My solution was to increase the dimensions and thereby its quality. 
            The classes, y target, are as previously stated: exp, lognorm, norm, and unif.

@@

            \begin{figure}

@@

            \end{figure}

            \begin{figure}

@@

            \end{figure}

            In order to properly evaluate the models, the accuracy and loss were not enough as indicators alone. 
            To this end, I saved all of the models and fed in the graph images they have not seen yet. 
            The models simply classified each image as natural or graph. First, I put the generated graphs in CIFAR\_SCP\_1. 
            The perfect outcome should be 100 percent since all 8,000 images are graphs. 
            The accuracy in this evaluation was 80.94 percent. 
            This could be much better but considering the high accuracy from GEN\_SCP\_1, 
            these graphs are not very similar. Next, the scraped graphs were put into CIFAR\_GEN\_1 
            and, like the above evaluation, should have a perfect accuracy of 100 percent. 
            The accuracy dropped even lower to 37.22 percent which is far from ideal. 
            What does this mean exactly? When graphs from the scraped dataset are put into the CIFAR\_GEN\_1, 
            it classifies most of them as natural images. 
            This outcome strengthens a hypothesis that quite a lot of scraped graphs are ‘graph-like’ 
            and are more similar to natural images. As the generated graphs are the main focus, 
            I took a deeper look at the falsely classified generated graphs in CIFAR\_SCP\_1. 
            The misclassifications were spread out pretty evenly, 
            but the graphs with uniform distribution were most often classified as natural images.

            Falsely Labeled Generated Graphs in CIFAR\_SCP\_1

@@

            \end{figure}

            After the training was finished, I saved all the models and fed all 8,000 graphs into the DIST\_153x115\_1 for evaluation. 
            I decided to stick with evaluating one model since doing the same process for all would have been redundant 
            and not given me further insights into the data and model performance. 
            I chose DIST\_153x115\_1 instead of the other two because it performed slightly better 
            but using DIST\_115x86 would have been viable as well. The saved DIST\_153x115\_1 model performed well in the evaluation 
            by accomplishing an accuracy of 96.54 percent. That means there were a total of 270 misclassifications out of 8,000 images. 
            The probability distribution with the most misclassifications was the exponential distribution at 149, 
            while the lowest was the uniform distribution with only 6 misclassifications. 
            Why were graphs with an exponential distribution most often labelled incorrectly 
            and by such a wide margin? A closer look at the data shows that almost all of the exponential distribution graphs 
            that were misclassified where misclassified as the log-normal distribution. 
            When one looks at the images in question then it is easier to see why that is the case, 
            but it is still noteworthy how high the accuracy is despite the similarities. 
            There were 2,000 exponential distribution graphs and only 147 were labeled as log-normal distribution 
            which still indicates a strong performance.

>>>>

    \renewcommand{\figurename}{Visual}
    \renewcommand{\tablename}{Visual}

@@

            \begin{table}[ht]

@@

@@

            In the end, four classes were kept, bar chart, diagram, graph, and pie chart, 
            so the total images now used were 7,753. 
            he images came in various dimensions and were resized to the natural images 32x32 and converted to JPG format. 
            I’ll note here that JPG was chosen because it only has 3 color channels and no alpha channel. 
            If PNG is used then it could have a shape of (32,32,4) which adds unnecessary parameters for the scope of my objectives.
            See Visual \ref{scraped-overview} for examples.

            \begin{table}[ht]

@@

            Early on, I pre-identified possible misclassifications once I scanned through the set of generated graphs. 
            The similarities between some of the graphs, especially the log-normal and normal distribution, were considerable. 
            They were not ‘duds’ like previously mentioned -- they looked typical, but because of the density functions’ parameters, 
            they were similar in appearance to a point where it would become a 50-50 decision if I had to classify them myself. 
            The cases when this happened are a minority, but it was important to keep this in mind as I evaluated the models later.
            See Visual \ref{generated-overview} for examples. The density functions that created the random variables in the graph
            are listed below.

            \begin{table}[ht]

@@

            The ANN process used in my model is called a feed-forward neural network or FNN. 
            The structure of the model consists of three parts and are shown in Visual \ref{nn-bishop}: 
            an input layer, one or many hidden layers consisting of neurons, and an output layer. 
            The two main processes in the model are forward-propagation and back-propagation, 
            and can be summed up by their respective goals, producing an estimate and minimizing the loss. 
            Forward-propagation begins once the model is built and the data is split into the input values x and the target values y. 
            In this scenario the goal is to use x to predict y.

@@

                The most important parts of a CNN are its convolutional layers and pooling layers 
                since they are the means in which the original image gets ‘boiled down’ into its ‘essence’.
                I use this analogy because one can imagine a set of ingredients, pixels making up an image, 
                that get thrown into a boiling pot where the water evaporates leaving only the important flavors behind. 
                This visceral example can be summed up more literally, 
                where the original image gets transformed layer by layer from the original pixel values to the final class scores. 
                By the end, the full image will be reduced into a single vector of class scores, arranged along the depth dimension. 
                What are these class scores? They indicate the estimate for each class or y target. 
                As an example, the final output layer for CIFAR-10 would have dimensions of (1, 1, 10) 
                since it has a total of 10 classes that an image can be sorted into \cite{cs231n2023} -- airplane, dog, cat, etc.
                The step by step process can be seen more clearly in Visual \ref{cnn-overview-fig},
                where the input image of car will be transformed into the most important features and then classified as a car.

                \begin{table}[ht]

@@

                \textbf{Output Volume Size Equation \cite{cs231n2023}:}

@@

            The implementation of this project wouldn’t be possible without the various tools used. 
            I’ll describe them all briefly and list out the versions used for the sake of reproducibility in Visual \ref{py-versions}. 
            TensorFlow \cite{abadi2016-tensorflow} is an end-to-end platform for building machine learning models 
            and that works with Keras \cite{chollet2015-keras}, which is a deep learning API written in Python connected to TensorFlow, 
            to create all of the models in this project. 
            Python comes with a plethora of libraries to make working with data and images easier. 
            First there is NumPy \cite{harris2020-numpy} -- a math library with powerful ndarrays. 
            Then there is pandas \cite{reback2020-pandas} \cite{mckinney2010-pandas} 
            which allows for the creation and manipulation of dataframes, which themselves are made up of NumPy’s arrays. 
            The next important library is Matplotlib \cite{hunter2007-matplotlib} 
            where all of the generated graphs used in the models were plotted. 
            Lastly, one of the most important libraires for image classification using TensorFlow 
            and Keras is Pillow \cite{clark2015pillow} since it allows the user to manipulate individual pixels of an image using Python. 
            The PIL Image is a class that can be used and returned using TensorFlow.

@@

            In total, four simple graph classifiers were created -- each with a specific purpose of evaluation in mind. 
            The idea behind them was to create a base assumption that the graphs I generated can be considered a realistic dataset 
            one could get if they scraped from various sources. 
            The main goal is to be able to classify graphs into their probability distribution, 
            but this step acts as a bridge and quality assurance for the generated graph dataset 
            which will be used in the distribution graph classifiers. 
            Each model has a specific name consisting of acronyms to distinguish itself: 
            CIFAR is the natural images, SCP is the scraped graphs, GEN stands for the generated graphs, 
            and 1 indicates the model structure. This results in the four models: CIFAR\_SCP\_1, CIFAR\_GEN\_1, GEN\_SCP\_1, 
            and CIFAR\_GEN\_SCP\_1. The model struture for all classifiers is shown by layer in Visual \ref{model-layer-info}.

@@

            The second model, much like the first one, answers the question: 
            are the generated graphs distinguishable from the natural images as well? 
            This was the first test for the generated graphs and much like the first model, 
            should have achieved high accuracy. The main question here would be the difference in accuracy between CIFAR\_SCP\_1 
            and CIFAR\_GEN\_1 since a higher accuracy in the former would indicate 
            that my generated graphs have some similarities with natural images that are not apparent in the scraped graphs. 
            This could be turned around and a much higher accuracy in CIFAR\_GEN\_1 could indicate 
            that one of my original theories about the scraped dataset could be correct 
            and that is the ‘graph-like’ nature of the images in the scraped dataset which are more artistic 
            or non-numerical representations of graphs. 
            In Visual \ref{cifar-graphs-1}, one can see that the input in CIFAR\_SCP\_1 and CIFAR\_GEN\_1 are balanced.

@@

            Lastly, all of the datasets were used in a model to classify them as natural, generated, or scraped. 
            The outcome of this would not be as important as the first three, 
            but it would have reinforced the previous intermediate conclusions about the nature of the datasets. 
            A very high accuracy would have meant all datasets are highly distinguishable from one another 
            and point towards tweaking the generated graphs. The information for GEN\_SCP\_1 and CIFAR\_GEN\_SCP\_1
            can be seen in Visual \ref{cifar-gen-scp-1}.

@@

            The images used, total number of images, training images, validation images, 
            and model structure are all the same, except for the dimensions of the image and that can be seen in Visual \ref{dist-dims-1}.
            The reason for this is how much information is lost when the image is 32x32. 
            It was easy to assume that the model would perform poorly when the density function line almost completely disappears. 
            My solution was to increase the dimensions and thereby its quality. 
            The classes, y target, are as previously stated: exp, lognorm, norm, and unif.

@@

            \begin{table}

@@

            \begin{table}

@@

            In order to properly evaluate the models, the accuracy and loss were not enough as indicators alone. 
            To this end, I saved all of the models and fed in the graph images they have not seen yet. 
            The models simply classified each image as natural or graph. First, I put the generated graphs in CIFAR\_SCP\_1. 
            The perfect outcome should be 100 percent since all 8,000 images are graphs. 
            The accuracy in this evaluation was 80.94 percent. 
            This could be much better but considering the high accuracy from GEN\_SCP\_1, 
            these graphs are not very similar. Next, the scraped graphs were put into CIFAR\_GEN\_1 
            and, like the above evaluation, should have a perfect accuracy of 100 percent. 
            The accuracy dropped even lower to 37.22 percent which is far from ideal. 
            What does this mean exactly? When graphs from the scraped dataset are put into the CIFAR\_GEN\_1, 
            it classifies most of them as natural images. 
            This outcome strengthens a hypothesis that quite a lot of scraped graphs are ‘graph-like’ 
            and are more similar to natural images. As the generated graphs are the main focus, 
            I took a deeper look at the falsely classified generated graphs in CIFAR\_SCP\_1. 
            The misclassifications were spread out pretty evenly, 
            but the graphs with uniform distribution were most often classified as natural images.
            The counts can be seen in Visual \ref{mis-gen-in-cifar-scp-1-chart} 
            and some examples of misclassified graphs are shown in Visual \ref{mis-gen-in-cifar-scp-1-examples}.

            \begin{table}

                    \includegraphics[scale=0.7]{misclassified-gen-in-cifar-scp-1.png}
                    \caption{Misclassified generated graphs in CIFAIR\_SCP\_1}
                    \label{mis-gen-in-cifar-scp-1-chart}

            \begin{table}
                \begin{center}

                    \begin{tabular}{ c  c }

                        \includegraphics[scale=0.74]{mis-as-nat-exp-20.jpg} & \includegraphics[scale=0.74]{mis-as-nat-lognorm-544.jpg} \\

                        \includegraphics[scale=0.74]{mis-as-nat-norm-695.jpg} & \includegraphics[scale=0.74]{mis-as-nat-unif-352.jpg} \\

                    \caption{Examples of misclassified generated graphs as natural images}
                    \label{mis-gen-in-cifar-scp-1-examples}

@@

            After the training was finished, I saved all the models and fed all 8,000 graphs into the DIST\_153x115\_1 for evaluation. 
            I decided to stick with evaluating one model since doing the same process for all would have been redundant 
            and not given me further insights into the data and model performance. 
            I chose DIST\_153x115\_1 instead of the other two because it performed slightly better 
            but using DIST\_115x86 would have been viable as well. The saved DIST\_153x115\_1 model performed well in the evaluation 
            by accomplishing an accuracy of 96.54 percent. That means there were a total of 270 misclassifications out of 8,000 images,
            and the results can be seen in Visual \ref{mis-all-count-in-dist} and Visual \ref{counts-all-gen-dist}.
            The probability distribution with the most misclassifications was the exponential distribution at 149, 
            while the lowest was the uniform distribution with only 6 misclassifications. 
            Why were graphs with an exponential distribution most often labelled incorrectly 
            and by such a wide margin? A closer look at the data in Visual \ref{mis-all-count-in-dist} shows that almost all of the exponential distribution graphs 
            that were misclassified where misclassified as the log-normal distribution. 
            When one looks at the images in question then it is easier to see why that is the case, 
            but it is still noteworthy how high the accuracy is despite the similarities. 
            There were 2,000 exponential distribution graphs and only 147 were labeled as log-normal distribution 
            which still indicates a strong performance.

            \begin{table}

                    \begin{tabular}{ c  c }

                        \includegraphics[scale=0.63]{mis-exp-count-in-dist.png} & \includegraphics[scale=0.63]{mis-lognorm-count-in-dist.png} \\

                        \includegraphics[scale=0.63]{mis-norm-count-in-dist.png} & \includegraphics[scale=0.63]{mis-unif-count-in-dist.png} \\

                    \caption{Counts of misclassified generated graphs in DIST\_153x115\_1}
                    \label{mis-all-count-in-dist}

            \begin{table}

                    \begin{tabular}{| l | c | c | c | c |}

                        \hline
                        \textbf{Prediction}   &    \textbf{Exp}   &   \textbf{Lognorm}   &    \textbf{Norm}    &    \textbf{Unif} \\
                        \hline
                        True                  & 1,851             & 1,925                & 1,960               & 1,994 \\
                        False                 & 149               & 75                   & 40                  & 6 \\

                        \hline

                    \caption{Counts of correctly and falsely classified generated graphs in DIST\_153x115\_1}
                    \label{counts-all-gen-dist}
